Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Add page number

> The important story about the 2011
Arab revolts in Tunisia, Egypt, and Libya is not how the globalization of the
norms of civic engagement shaped the protesters' aspirations. Nor is it about
how activists used technology to share ideas and tactics. Instead, the critical
issue is how and why these ambitions and techniques resonated in their various
local contexts. [anderson2011demystifying]

@@

The concept of lexical, or semantic, cohesion has already been applied to the
analysis of political speech (for example, the language of Margaret Thatcher) 
and non-political speech [@barzilay1999using; @morris1991lexical].

The words that comprise social media posts are the first level at which cohesion
occurs. In Figure \@ref(fig:cohesion-in-tweets), we see four sequential tweets, 
each containing four words.
Each sequential tweet contains some content included in the previous tweets. The
linguistic construct of content word overlap measures the relationship across
units of meaning---here, tweets---where identical and semantically similar words
are repeated [@graesser2004coh]. These repeated lexical
items constitute a theme; on Twitter, this might be a particular hashtag, a
name, a location, or other nominal category. This localized cohesion is
referential; words are repeated and co-referred across tweets, creating a sense
of continuity and cohesiveness of meaning and message.

@@

#### Cohesion in Social Movements and Civil Wars
People join social and political resistance movements because they feel a sense
of connection to the cause, and because they have been sufficiently convinced to
participate. Given that people are generally risk averse, overcoming inertia
requires a strong connection to the group identity, or against an individual,
event, or political injustice [@Goldstone_1980; Goldstone_2011]. Political
resistance offers participants the opportunity to “lose themselves” and
relinquish their individual identity in favor of identification with a larger
group identity, thus contributing to a cohesive group ready and mobilized for
action [@Hoffer_2011. Previous research on social movements supports the idea
that participants are likely to join movements when they know and have a
personal connection to someone else already involved [@McAdam_1986. The type of
collective contentious behavior that manifests in society is a function of the
available political opportunity structures. The political opportunity structure,
as defined by Kitschelt (1986) are “comprised of specific configuration of
resources, institutional arrangements and historical precedents for social
mobilization, which facilitate the development of protest movements in some
instances and constrain them in others [@Kitschelt_1986].” What emerges as
strategies and tactics in contentious politics is in essence, a function of what
the system makes possible. This includes the number of people and their
disposition, i.e. nonviolent or violent, as well as their internal structure.
The more cohesive a group is, the greater threat they pose to the establishment.

>>>>

> The important story about the 2011
Arab revolts in Tunisia, Egypt, and Libya is not how the globalization of the
norms of civic engagement shaped the protesters' aspirations. Nor is it about
how activists used technology to share ideas and tactics. Instead, the critical
issue is how and why these ambitions and techniques resonated in their various
local contexts. [@anderson2011demystifying]

@@

The words that comprise social media posts are the first level of cohesion that
we will consider. The concept of lexical, or semantic, cohesion has already been
applied to the analysis of political speech (for example, the language of
Margaret Thatcher) and non-political speech [@barzilay1999using;
@morris1991lexical]. In Figure \@ref(fig:cohesion-in-tweets), we see four
sequential tweets, each containing four words.
Each sequential tweet contains some content included in the previous tweets. The
linguistic construct of content word overlap measures the relationship across
units of meaning---here, tweets---where identical and semantically similar words
are repeated [@graesser2004coh]. These repeated lexical
items constitute a theme; on Twitter, this might be a particular hashtag, a
name, a location, or other nominal category. This localized cohesion is
referential; words are repeated and co-referred across tweets, creating a sense
of continuity and cohesiveness of meaning and message.

@@

#### Cohesion in Social Movements and Civil Wars
People join social and political resistance movements because they feel a sense
of connection to the cause, and because they have been sufficiently convinced to
participate. Given that people are generally risk averse, overcoming inertia
requires a strong connection to the group identity, or against an individual,
event, or political injustice [@Goldstone_1980; Goldstone_2011]. Political
resistance offers participants the opportunity to “lose themselves” and
relinquish their individual identity in favor of identification with a larger
group identity, thus contributing to a cohesive group ready and mobilized for
action [@Hoffer_2011. Previous research on social movements supports the idea
that participants are likely to join movements when they know and have a
personal connection to someone else already involved [@McAdam_1986. The type of
collective contentious behavior that manifests in society is a function of the
available political opportunity structures. The political opportunity structure,
as defined by Kitschelt (1986) are “comprised of specific configuration of
resources, institutional arrangements and historical precedents for social
mobilization, which facilitate the development of protest movements in some
instances and constrain them in others” [@Kitschelt_1986, p. 58]. What emerges
as strategies and tactics in contentious politics is in essence, a function of
what the system makes possible. This includes the number of people and their
disposition, i.e. nonviolent or violent, as well as their internal structure.
The more cohesive a group is, the greater threat they pose to the establishment.
